Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-06-15 FIE2019-final-TPJHD.tex
tweaks to challenges intro and PCI section

Is teaching cybersecurity different? Lecturing is probably not the best way. Should we use real-life case studies (e.g. British Airways \cite{Barth2018a}).  % JHD - need's fixing.

%AI noted the workshops with ISC$^2$, with the ``this is a fad'' concept.  {\bf AI to write up}.
  This raises pedagogic questions which are beyond the scope of this research to resolve. Should we be teaching content because it's underpinning?; or because there's a skill shortage?

@@

\subsection{An industry example - PCI DSS}\label{sec:PCIDSS}
The Payments Card Industry Data Security Standards \cite{PCI2018b} underpin all processing of credit/debit cards. Nevertheless, they are very rarely mentioned in generalist computer scientist courses --- one payments industry person commented ``I've given up even asking if recruits have heard of PCI DSS: it's so rare''.

This would not matter so much if everyone handling payments data were sent by their employers on an effective\footnote{``Effective'' is important: the Processing Director at one major acquirer commented ``I just caught two developers in the elevator discussing how to meet a customer requirement, and I had to tell them this was contrary to PCI DSS. Their response was that the customer wanted it!''.} PCI DSS course. However, the payments business is now so spread across websites, often run by SMEs, or non-specialists, that some provision should be made in courses.  Even larger enterprises are not immune: \cite{Barth2018a} reports that the recent British Airways breach was caused by a failure to adhere to PCI DSS in the website maintenance.

%Alastair to write about their Credit Fraud experience (MSc cybersecurity).  HE Academy grant (to be referenced).

>>>>

Is teaching cybersecurity different? Lecturing is probably not the best way. Should we use real-life case studies (e.g. British Airways \cite{Barth2018a}). \cite{Weiss:2013:THC:2527148.2527180} suggests that there are benefits from teaching this discipline area in a more practical manner.

%AI noted the workshops with ISC$^2$, with the ``this is a fad'' concept.  {\bf AI to write up}.
  % Should we remove this?  This raises pedagogic questions which are beyond the scope of this research to resolve. Should we be teaching content because it's underpinning?; or because there's a skill shortage?

@@

\subsection{Industry standards - Payments Card Industry Data Security Standards (PCI DSS)}\label{sec:PCIDSS}
The PCI DSS \cite{PCI2018b} underpin all processing of credit/debit cards. Nevertheless, they are very rarely mentioned in generalist computer scientist courses. This would not matter so much if everyone handling payments data were sent by their employers on an effective PCI DSS course. However, the payments business is now so spread across websites, often run by small and medium enterprises (SME), or non-specialists.  Even larger enterprises are not immune: \cite{Barth2018a} reports that the recent British Airways breach was caused by a failure to adhere to PCI DSS in the website maintenance. It is an interesting question as to whether standards such as PCI DSS should be addressed within degree courses (clearly degree courses can never cover all standards) or whether they should be addressed in professional training courses. However it appears the current situation is not ideal.
